Observed vs. Simulated Year Comparison

### 2022-09-16 03-post-process/compare-sim-to-obs.Rmd
Add quantities to sim vs. obs comparison
Previously, these quantities were only shown in aggregate within a population; the finer resolution has already helped to pinpoint where some issues may be.

* Adult return to estuary by origin
* Adult return to tributary by origin
* Spawners by origin
* Total egg production by origin
* Eggs per spawner by origin
* Proportion hatchery return by age
* Age composition by origin

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.align = "center", fig.width = 8, fig.height = 4)
knitr::opts_knit$set(root.dir = "../")
```

@@

# extract the model data 
jags_data = model_info$jags_data
```

@@

```{r add-Rb-tot}
# extract spawners returning to tributary
Rb = post_subset(post, "^Rb[", matrix = TRUE)

# for each posterior sample, calculate the fraction that are hatchery origin
out = NULL
for (i in 1:nrow(Rb)) {
  Rb_i = array_format(Rb[i,])
  nor = Rb_i[,1,1,] + Rb_i[,2,1,] + Rb_i[,3,1,]
  hor = Rb_i[,1,2,] + Rb_i[,2,2,] + Rb_i[,3,2,]
  out = rbind(out, as.numeric(nor + hor))
}

@@

# make element names
colnames(out) = paste0("Rb_tot[", r_ind, ",", c_ind, "]")

@@

@@

  # reorder rows
  x$Class = factor(x$Class, levels = c("FW Juvenile", "SW Juvenile", "FW Adult"))
  x$Type = factor(x$Type, levels = c("Egg to Parr Survival", "Parr Mean Size", "Proportion Fall Migrants", "Overwinter Survival", "Parr to Smolt Mean Size 'Growth Factor'", "Smolt Mean Size", "Migration to LGR Survival", "LGR to Ocean Survival", "First Year Ocean Survival", "Age-3 Maturity", "Age-4 Maturity", "BON to LGR Survival", "Pre-Spawn Survival"))
  x$LH_type = factor(x$LH_type, levels = c("Combined", "Fall", "Spring"))
  x$origin = factor(x$origin, levels = c("Combined", "NOR", "HOR"))
  x = x[order(x$Class, x$Type, x$LH_type, x$origin),]

@@

  # reorder rows
  x$Class = factor(x$Class, levels = c("Abundance", "Production Rates", "SAR", "Adult Composition"))
  x$Type = factor(x$Type, levels = c("Total Adults (Estuary)", "Total Adults (To Tributary)", "Total Spawners", "Total Egg Production", "Total Parr Recruitment", "Total LGR Smolt", "Aggregate Total Adult Return (To Tributary)", "Aggregate Total Smolt (At LGR)", "Parr per Spawner", "Smolt in Tributary per Spawner", "Spawners per Spawner", "Smolt in Tributary per Parr", "Smolt at LGR per Parr", "BON to BON", "LGR to LGR", "Proportion Hatchery Return", "Proportion Age-3 Return", "Proportion Age-4 Return", "Proportion Age-5 Return"))
  x$LH_type = factor(x$LH_type, levels = c("Combined", "Fall", "Spring"))
  x$origin = factor(x$origin, levels = c("Combined", "NOR", "HOR"))
  x = x[order(x$Class, x$Type, x$LH_type, x$origin),]

@@

For us to use the state-space model as a simulation model, it would be desirable if several characteristics of the distribution of stochastic and derived quantities were similar between the time periods with and without observations.

This document is intended to identify whether simulated outcomes are similar to observed outcomes. It looks at two primary types of quantities: stochastic time series parameters that are directly estimated by the model (e.g., egg to parr survival fluctuations not attributable to density dependence) and emergent outcomes calculated as derived quantities from stochastic parameters (e.g., total adult return abundance, BON to BON SAR rates, etc.). Because all emergent outcomes are derived from the stochastic elements, issues with emergent outcomes should be traceable to specific stochastic parents.

@@

```{r}
x = lapply(1:4, function(j) get_ratio("^Rb_tot[year,pop]", obs_y, sim_y, pop = j))
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Total Adults (Estuary): Estimates")
ratio_plots(x, "Total Adults (Estuary): Ratios")
derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Abundance", Type = "Total Adults (Estuary)"))
```

@@

```{r}
x = lapply(1:4, function(j) get_ratio("^Ra_tot[year,pop]", obs_y, sim_y, pop = j))
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Total Adults (Tributary): Estimates")
ratio_plots(x, "Total Adults (Tributary): Ratios")
derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Abundance", Type = "Total Adults (To Tributary)"))
```

@@

```{r}
x = lapply(1:4, function(j) get_ratio("^Sa_tot[year,pop]", obs_y, sim_y, pop = j))
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Total Spawners: Estimates")
ratio_plots(x, "Total Spawners: Ratios")
derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Abundance", Type = "Total Spawners"))
```

@@

```{r}
x = lapply(1:4, function(j) get_ratio("^E[year,pop]", obs_y, sim_y, pop = j))
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Total Egg Production: Estimates")
ratio_plots(x, "Total Egg Production: Ratios")
derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Abundance", Type = "Total Egg Production"))
```

@@

@@

#### Proportion Hatchery Return

```{r}
x = lapply(1:4, function(j) get_ratio("p_hor[year,pop]", obs_y, sim_y, pop = j))
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Proportion Hatchery Return: Estimates")
ratio_plots(x, "Proportion Hatchery Return: Ratios")
derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Adult Composition", Type = "Proportion Hatchery Return"))
```

@@

```{r}
x = append(
  lapply(1:4, function(j) get_ratio("Ra_comp[year,age,origin,pop]", obs_y, sim_y, age = 1, origin = 1, pop = j)),
  lapply(1:4, function(j) get_ratio("Ra_comp[year,age,origin,pop]", obs_y, sim_y, age = 1, origin = 2, pop = j))
)
x = do.call(abind, append(x, list(along = 4)))
x[x == "Inf"] = 1; x[x == "NaN"] = 1
vals_plots(x, "Proportion Age-3 Return: Estimates")
ratio_plots(x, "Proportion Age-3 Return: Ratios")
derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Adult Composition", Type = "Proportion Age-3 Return"))
```

@@

```{r}
x = append(
  lapply(1:4, function(j) get_ratio("Ra_comp[year,age,origin,pop]", obs_y, sim_y, age = 2, origin = 1, pop = j)),
  lapply(1:4, function(j) get_ratio("Ra_comp[year,age,origin,pop]", obs_y, sim_y, age = 2, origin = 2, pop = j))
)
x = do.call(abind, append(x, list(along = 4)))
x[x == "Inf"] = 1; x[x == "NaN"] = 1
vals_plots(x, "Proportion Age-4 Return: Estimates")
ratio_plots(x, "Proportion Age-4 Return: Ratios")
derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Adult Composition", Type = "Proportion Age-4 Return"))
```

@@

```{r}
x = append(
  lapply(1:4, function(j) get_ratio("Ra_comp[year,age,origin,pop]", obs_y, sim_y, age = 3, origin = 1, pop = j)),
  lapply(1:4, function(j) get_ratio("Ra_comp[year,age,origin,pop]", obs_y, sim_y, age = 3, origin = 2, pop = j))
)
x = do.call(abind, append(x, list(along = 4)))
x[x == "Inf"] = 1; x[x == "NaN"] = 1
vals_plots(x, "Proportion Age-5 Return: Estimates")
ratio_plots(x, "Proportion Age-5 Return: Ratios")
derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Adult Composition", Type = "Proportion Age-5 Return"))
```

@@

@@

@@

@@

@@

@@

#### Proportion Hatchery Return

@@

@@

@@

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.align = "center", fig.width = 8, fig.height = 4, warning = FALSE)
knitr::opts_knit$set(root.dir = "../")
```

@@

# extract the model data 
jags_data = model_info$jags_data

o_nor = 1   # o = 1 is NOR
o_hor = 2   # o = 2 is HOR
k_3 = 1     # k = 1 is age-3
k_4 = 2     # k = 2 is age-4
k_5 = 3     # k = 3 is age-5
j_cat = 1   # j = 1 is CAT
j_los = 2   # j = 2 is LOS
j_min = 3   # j = 3 is MIN
j_ugr = 4   # j = 4 is UGR
```

@@

```{r add-p-hos-age}
# extract spawners returning to tributary
Ra = post_subset(post, "^Ra[", matrix = TRUE)

# for each posterior sample, calculate the fraction that are hatchery origin
out_3 = out_4 = out_5 = NULL
for (i in 1:nrow(Ra)) {
  Ra_i = array_format(Ra[i,])

  p_hor_3 = Ra_i[,k_3,o_hor,]/(Ra_i[,k_3,o_nor,] + Ra_i[,k_3,o_hor,])
  p_hor_4 = Ra_i[,k_4,o_hor,]/(Ra_i[,k_4,o_nor,] + Ra_i[,k_4,o_hor,])
  p_hor_5 = Ra_i[,k_5,o_hor,]/(Ra_i[,k_5,o_nor,] + Ra_i[,k_5,o_hor,])

  out_3 = rbind(out_3, as.numeric(p_hor_3))
  out_4 = rbind(out_4, as.numeric(p_hor_4))
  out_5 = rbind(out_5, as.numeric(p_hor_5))
}

# build the row indices for each element: the year
r_ind = rep(1:nrow(p_hor_3), ncol(p_hor_3))

# build the column indices for each element: the population
c_ind = rep(1:ncol(p_hor_3), each = nrow(p_hor_3))

# make element names
colnames(out_3) = paste0("p_hor_a[", r_ind, ",1,", c_ind, "]")
colnames(out_4) = paste0("p_hor_a[", r_ind, ",2,", c_ind, "]")
colnames(out_5) = paste0("p_hor_a[", r_ind, ",3,", c_ind, "]")
out = cbind(out_3, out_4, out_5)

```{r add-Rb-tot-origin}
# extract returns to estuary
Rb = post_subset(post, "^Rb[", matrix = TRUE)

# for each posterior sample, calculate the abundance by origin and total
out_tot = out_nor = out_hor = NULL
for (i in 1:nrow(Rb)) {
  Rb_i = array_format(Rb[i,])
  nor = Rb_i[,1,1,] + Rb_i[,2,1,] + Rb_i[,3,1,]
  hor = Rb_i[,1,2,] + Rb_i[,2,2,] + Rb_i[,3,2,]
  tot = nor + hor

  out_nor = rbind(out_nor, as.numeric(nor))
  out_hor = rbind(out_hor, as.numeric(hor))
  out_tot = rbind(out_tot, as.numeric(tot))
}

@@

# make element names
colnames(out_nor) = paste0("Rb_tot_org[", r_ind, ",1,", c_ind, "]")
colnames(out_hor) = paste0("Rb_tot_org[", r_ind, ",2,", c_ind, "]")
colnames(out_tot) = paste0("Rb_tot[", r_ind, ",", c_ind, "]")
out = cbind(out_nor, out_hor, out_tot)

```{r add-Ra-tot-origin}
# extract returns to tributary
Ra = post_subset(post, "^Ra[", matrix = TRUE)

# for each posterior sample, calculate the abundance by origin and total
out_nor = out_hor = NULL
for (i in 1:nrow(Ra)) {
  Ra_i = array_format(Ra[i,])
  nor = Ra_i[,1,1,] + Ra_i[,2,1,] + Ra_i[,3,1,]
  hor = Ra_i[,1,2,] + Ra_i[,2,2,] + Ra_i[,3,2,]

  out_nor = rbind(out_nor, as.numeric(nor))
  out_hor = rbind(out_hor, as.numeric(hor))
}

# make element names
colnames(out_nor) = paste0("Ra_tot_org[", r_ind, ",1,", c_ind, "]")
colnames(out_hor) = paste0("Ra_tot_org[", r_ind, ",2,", c_ind, "]")
out = cbind(out_nor, out_hor)

```{r add-Sa-tot-origin}
# extract spawners
Sa = post_subset(post, "^Sa[", matrix = TRUE)

# for each posterior sample, calculate the abundance by origin and total
out_nor = out_hor = NULL
for (i in 1:nrow(Ra)) {
  Sa_i = array_format(Sa[i,])
  nor = Sa_i[,1,1,] + Sa_i[,2,1,] + Sa_i[,3,1,]
  hor = Sa_i[,1,2,] + Sa_i[,2,2,] + Sa_i[,3,2,]

  out_nor = rbind(out_nor, as.numeric(nor))
  out_hor = rbind(out_hor, as.numeric(hor))
}

# make element names
colnames(out_nor) = paste0("Sa_tot_org[", r_ind, ",1,", c_ind, "]")
colnames(out_hor) = paste0("Sa_tot_org[", r_ind, ",2,", c_ind, "]")
out = cbind(out_nor, out_hor)

```{r add-E-origin}
E = post_subset(post, "^E_sep[", matrix = TRUE)

out_nor = out_hor = NULL
for (i in 1:nrow(Ra)) {
  E_i = array_format(E[i,])
  E_nor_i = E_i[,1,1,] + E_i[,2,1,] + E_i[,3,1,]
  E_hor_i = E_i[,1,2,] + E_i[,2,2,] + E_i[,3,2,]

  out_nor = rbind(out_nor, as.numeric(E_nor_i))
  out_hor = rbind(out_hor, as.numeric(E_hor_i))
}

# make element names
colnames(out_nor) = paste0("E_org[", r_ind, ",1,", c_ind, "]")
colnames(out_hor) = paste0("E_org[", r_ind, ",2,", c_ind, "]")
out = cbind(out_nor, out_hor)

```{r add-E-per-Sa-origin}
Sa = post_subset(post, "^Sa[", matrix = TRUE)
E = post_subset(post, "^E_sep[", matrix = TRUE)

out_nor = out_hor = NULL
for (i in 1:nrow(Ra)) {
  Sa_i = array_format(Sa[i,])
  Sa_nor_i = Sa_i[,1,1,] + Sa_i[,2,1,] + Sa_i[,3,1,]
  Sa_hor_i = Sa_i[,1,2,] + Sa_i[,2,2,] + Sa_i[,3,2,]
  E_i = array_format(E[i,])
  E_nor_i = E_i[,1,1,] + E_i[,2,1,] + E_i[,3,1,]
  E_hor_i = E_i[,1,2,] + E_i[,2,2,] + E_i[,3,2,]

  out_nor = rbind(out_nor, as.numeric(E_nor_i/Sa_nor_i))
  out_hor = rbind(out_hor, as.numeric(E_hor_i/Sa_hor_i))
}

# make element names
colnames(out_nor) = paste0("E_per_Sa_org[", r_ind, ",1,", c_ind, "]")
colnames(out_hor) = paste0("E_per_Sa_org[", r_ind, ",2,", c_ind, "]")
out = cbind(out_nor, out_hor)

@@

```{r add-age-comp-combined}
Ra = post_subset(post, "^Ra[", matrix = TRUE)

p3_out = p4_out = p5_out = NULL
for (i in 1:nrow(Ra)) {
  Ra_i = array_format(Ra[i,])

  a3_tot = Ra_i[,1,1,] + Ra_i[,1,2,]
  a4_tot = Ra_i[,2,1,] + Ra_i[,2,2,]
  a5_tot = Ra_i[,3,1,] + Ra_i[,3,2,]
  tot = a3_tot + a4_tot + a5_tot

  p3 = Ra_i[,1,1,]/tot
  p4 = Ra_i[,2,1,]/tot
  p5 = Ra_i[,3,1,]/nor_tot

  p3_out = rbind(p3_out, as.numeric(p3))
  p4_out = rbind(p4_out, as.numeric(p4))
  p5_out = rbind(p5_out, as.numeric(p5))
}

# build the row indices for each element: the year
r_ind = rep(1:nrow(p3), ncol(p3))

# build the column indices for each element: the population
c_ind = rep(1:ncol(p3), each = nrow(p3))

# make element names
colnames(p3_out) = paste0("Ra_comp_a[", r_ind, ",", "1", ",", c_ind, "]")
colnames(p4_out) = paste0("Ra_comp_a[", r_ind, ",", "2", ",", c_ind, "]")
colnames(p5_out) = paste0("Ra_comp_a[", r_ind, ",", "3", ",", c_ind, "]")

out = cbind(p3_out, p4_out, p5_out)

@@

  # reorder rows
  x$Class = factor(x$Class, levels = c("FW Juvenile", "SW Juvenile", "FW Adult"))
  x$Type = factor(x$Type, levels = c("Egg to Parr Survival", "Parr Mean Size", "Proportion Fall Migrants", "Overwinter Survival", "Parr to Smolt Mean Size 'Growth Factor'", "Smolt Mean Size", "Migration to LGR Survival", "LGR to Ocean Survival", "First Year Ocean Survival", "Age-3 Maturity", "Age-4 Maturity", "BON to LGR Survival", "Pre-Spawn Survival"))
  x$LH_type = factor(x$LH_type, levels = c("Combined", "Fall", "Spring"))
  x$origin = factor(x$origin, levels = c("NOR", "HOR", "Combined"))
  x = x[order(x$Class, x$Type, x$LH_type, x$origin),]

@@

  # reorder rows
  x$Class = factor(x$Class, levels = c("Abundance", "Production Rates", "SAR", "Adult Composition"))
  x$Type = factor(x$Type, levels = c("Total Adults (Estuary)", "Total Adults (To Tributary)", "Total Spawners", "Total Egg Production", "Total Parr Recruitment", "Total LGR Smolt", "Aggregate Total Adult Return (To Tributary)", "Aggregate Total Smolt (At LGR)", "Eggs per Spawner", "Parr per Spawner", "Smolt in Tributary per Spawner", "Spawners per Spawner", "Smolt in Tributary per Parr", "Smolt at LGR per Parr", "BON to BON", "LGR to LGR", "Proportion Hatchery Return (Age-3)", "Proportion Hatchery Return (Age-4)", "Proportion Hatchery Return (Age-5)", "Proportion Hatchery Return (All Ages)", "Proportion Age-3 Return", "Proportion Age-4 Return", "Proportion Age-5 Return"))
  x$LH_type = factor(x$LH_type, levels = c("Combined", "Fall", "Spring"))
  x$origin = factor(x$origin, levels = c("NOR", "HOR", "Combined"))
  x = x[order(x$Class, x$Type, x$LH_type, x$origin),]

  colnames(x)[which(colnames(x) == "LH_type")] = "Mig. Type"
  colnames(x)[which(colnames(x) == "origin")] = "Origin"

@@

For us to use the state-space model as a simulation model (which is the ultimate intent), it would be desirable if several characteristics of the distribution of stochastic and derived quantities were similar between the time periods with and without observations.

This document is intended to identify whether outcomes simulated from the state-space model are similar to observed outcomes.
It looks at two primary types of quantities: stochastic time series parameters that are directly estimated by the model (e.g., egg to parr survival fluctuations not attributable to density dependence) and emergent outcomes calculated as derived quantities from stochastic parameters (e.g., total adult return abundance, BON to BON SAR rates, etc.). Because all emergent outcomes are derived from the stochastic elements, issues with emergent outcomes should be traceable to specific stochastic parents.

@@

```{r}
# by origin: plot and table
x = append(
  lapply(1:4, function(j) get_ratio("Rb_tot_org[year,origin,pop]", obs_y, sim_y, pop = j, origin = 1)),
  lapply(1:4, function(j) get_ratio("Rb_tot_org[year,origin,pop]", obs_y, sim_y, pop = j, origin = 2))
)
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Total Adults (Estuary): Estimates")
ratio_plots(x, "Total Adults (Estuary): Ratios")
derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Abundance", Type = "Total Adults (Estuary)"))
```

```{r}
# combined: table only
x = lapply(1:4, function(j) get_ratio("^Rb_tot[year,pop]", obs_y, sim_y, pop = j))
x = do.call(abind, append(x, list(along = 4)))
derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Abundance", Type = "Total Adults (Estuary)"))
```

@@

```{r}
# by origin: plot and table
x = append(
  lapply(1:4, function(j) get_ratio("Ra_tot_org[year,origin,pop]", obs_y, sim_y, pop = j, origin = 1)),
  lapply(1:4, function(j) get_ratio("Ra_tot_org[year,origin,pop]", obs_y, sim_y, pop = j, origin = 2))
)
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Total Adults (Tributary): Estimates")
ratio_plots(x, "Total Adults (Tributary): Ratios")
derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Abundance", Type = "Total Adults (To Tributary)"))
```

```{r}
# combined: table only
x = lapply(1:4, function(j) get_ratio("^Ra_tot[year,pop]", obs_y, sim_y, pop = j))
x = do.call(abind, append(x, list(along = 4)))
derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Abundance", Type = "Total Adults (To Tributary)"))
```

@@

```{r}
# by origin: plot and table
x = append(
  lapply(1:4, function(j) get_ratio("Sa_tot_org[year,origin,pop]", obs_y, sim_y, pop = j, origin = 1)),
  lapply(1:4, function(j) get_ratio("Sa_tot_org[year,origin,pop]", obs_y, sim_y, pop = j, origin = 2))
)
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Total Spawners: Estimates")
ratio_plots(x, "Total Spawners: Ratios")
derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Abundance", Type = "Total Spawners"))
```

```{r}
# combined: table only
x = lapply(1:4, function(j) get_ratio("^Sa_tot[year,pop]", obs_y, sim_y, pop = j))
x = do.call(abind, append(x, list(along = 4)))
derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Abundance", Type = "Total Spawners"))
```

@@

```{r}
# by origin: plot and table
x = append(
  lapply(1:4, function(j) get_ratio("^E_org[year,origin,pop]", obs_y, sim_y, pop = j, origin = 1)),
  lapply(1:4, function(j) get_ratio("^E_org[year,origin,pop]", obs_y, sim_y, pop = j, origin = 2))
)
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Total Egg Production: Estimates")
ratio_plots(x, "Total Egg Production: Ratios")
derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Abundance", Type = "Total Egg Production"))
```

```{r}
# combined: table only
x = lapply(1:4, function(j) get_ratio("^E[year,pop]", obs_y, sim_y, pop = j))
x = do.call(abind, append(x, list(along = 4)))
derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Abundance", Type = "Total Egg Production"))
```

@@

#### Eggs per Spawner

```{r}
# by origin: plot and table
x = append(
  lapply(1:4, function(j) get_ratio("E_per_Sa_org[year,origin,pop]", obs_y, sim_y, pop = j, origin = 1)),
  lapply(1:4, function(j) get_ratio("E_per_Sa_org[year,origin,pop]", obs_y, sim_y, pop = j, origin = 2))
)
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Eggs per Spawner: Estimates")
ratio_plots(x, "Eggs per Spawner: Ratios")
derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Production Rates", Type = "Eggs per Spawner"))
```

```{r}
# combined: table only
x = lapply(1:4, function(j) get_ratio("^E_per_Sa[year,pop]", obs_y, sim_y, pop = j))
x = do.call(abind, append(x, list(along = 4)))
derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Production Rates", Type = "Eggs per Spawner"))
```

@@

#### Proportion Hatchery Return {.tabset .tabset-pills}

##### Age-3

```{r}
x = lapply(1:4, function(j) get_ratio("p_hor_a[year,age,pop]", obs_y, sim_y, age = 1, pop = j))
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Proportion Hatchery Return (Age-3): Estimates")
ratio_plots(x, "Proportion Hatchery Return (Age-3): Ratios")
derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Adult Composition", Type = "Proportion Hatchery Return (Age-3)"))
```

##### Age-4

```{r}
x = lapply(1:4, function(j) get_ratio("p_hor_a[year,age,pop]", obs_y, sim_y, age = 2, pop = j))
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Proportion Hatchery Return (Age-4): Estimates")
ratio_plots(x, "Proportion Hatchery Return (Age-4): Ratios")
derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Adult Composition", Type = "Proportion Hatchery Return (Age-4)"))
```

##### Age-5

```{r}
x = lapply(1:4, function(j) get_ratio("p_hor_a[year,age,pop]", obs_y, sim_y, age = 3, pop = j))
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Proportion Hatchery Return (Age-5): Estimates")
ratio_plots(x, "Proportion Hatchery Return (Age-5): Ratios")
derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Adult Composition", Type = "Proportion Hatchery Return (Age-5)"))
```

##### All Ages

```{r}
x = lapply(1:4, function(j) get_ratio("p_hor[year,pop]", obs_y, sim_y,  pop = j))
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Proportion Hatchery Return (All Ages): Estimates")
ratio_plots(x, "Proportion Hatchery Return (All Ages): Ratios")
derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Adult Composition", Type = "Proportion Hatchery Return (All Ages)"))
```

@@

```{r}
# by origin: plot and table
x = append(
  lapply(1:4, function(j) get_ratio("Ra_comp[year,age,origin,pop]", obs_y, sim_y, age = 1, origin = 1, pop = j)),
  lapply(1:4, function(j) get_ratio("Ra_comp[year,age,origin,pop]", obs_y, sim_y, age = 1, origin = 2, pop = j))
)
x = do.call(abind, append(x, list(along = 4)))
x[x == "Inf"] = 1; x[x == "NaN"] = 1
vals_plots(x, "Proportion Age-3 Return: Estimates")
ratio_plots(x, "Proportion Age-3 Return: Ratios")
derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Adult Composition", Type = "Proportion Age-3 Return"))
```

```{r}
# combined: table only
x = lapply(1:4, function(j) get_ratio("^Ra_comp_a[year,age,pop]", obs_y, sim_y, pop = j, age = 1))
x = do.call(abind, append(x, list(along = 4)))
derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Adult Composition", Type = "Proportion Age-3 Return"))
```

@@

```{r}
# by origin: plot and table
x = append(
  lapply(1:4, function(j) get_ratio("Ra_comp[year,age,origin,pop]", obs_y, sim_y, age = 2, origin = 1, pop = j)),
  lapply(1:4, function(j) get_ratio("Ra_comp[year,age,origin,pop]", obs_y, sim_y, age = 2, origin = 2, pop = j))
)
x = do.call(abind, append(x, list(along = 4)))
x[x == "Inf"] = 1; x[x == "NaN"] = 1
vals_plots(x, "Proportion Age-4 Return: Estimates")
ratio_plots(x, "Proportion Age-4 Return: Ratios")
derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Adult Composition", Type = "Proportion Age-4 Return"))
```

```{r}
# combined: table only
x = lapply(1:4, function(j) get_ratio("^Ra_comp_a[year,age,pop]", obs_y, sim_y, pop = j, age = 2))
x = do.call(abind, append(x, list(along = 4)))
derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Adult Composition", Type = "Proportion Age-4 Return"))
```

@@

```{r}
# by origin: plot and table
x = append(
  lapply(1:4, function(j) get_ratio("Ra_comp[year,age,origin,pop]", obs_y, sim_y, age = 3, origin = 1, pop = j)),
  lapply(1:4, function(j) get_ratio("Ra_comp[year,age,origin,pop]", obs_y, sim_y, age = 3, origin = 2, pop = j))
)
x = do.call(abind, append(x, list(along = 4)))
x[x == "Inf"] = 1; x[x == "NaN"] = 1
vals_plots(x, "Proportion Age-5 Return: Estimates")
ratio_plots(x, "Proportion Age-5 Return: Ratios")
derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Adult Composition", Type = "Proportion Age-5 Return"))
```

```{r}
# combined: table only
x = lapply(1:4, function(j) get_ratio("^Ra_comp_a[year,age,pop]", obs_y, sim_y, pop = j, age = 3))
x = do.call(abind, append(x, list(along = 4)))
derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Adult Composition", Type = "Proportion Age-5 Return"))
```

@@

#### Total Adult Return (To Estuary) {.tabset .tabset-pills}

```{r}
pop_ts_plots("^Rb_tot_org[year,origin,pop]", origin = 1)
```

```{r}
pop_ts_plots("^Rb_tot_org[year,origin,pop]", origin = 2)
```

##### Combined

@@

#### Total Adult Return (To Tributary) {.tabset .tabset-pills}

```{r}
pop_ts_plots("^Ra_tot_org[year,origin,pop]", origin = 1)
```

```{r}
pop_ts_plots("^Ra_tot_org[year,origin,pop]", origin = 2)
```

##### Combined

@@

#### Total Spawners {.tabset .tabset-pills}

```{r}
pop_ts_plots("^Sa_tot_org[year,origin,pop]", origin = 1)
```

```{r}
pop_ts_plots("^Sa_tot_org[year,origin,pop]", origin = 2)
```

##### Combined

@@

#### Total Egg Production {.tabset .tabset-pills}

```{r}
pop_ts_plots("^E_org[year,origin,pop]", origin = 1)
```

```{r}
pop_ts_plots("^E_org[year,origin,pop]", origin = 2)
```

##### Combined

@@

#### Eggs per Spawner {.tabset .tabset-pills}

```{r}
pop_ts_plots("^E_per_Sa_org[year,origin,pop]", origin = 1)
```

```{r}
pop_ts_plots("^E_per_Sa_org[year,origin,pop]", origin = 2)
```

##### Combined

```{r}
pop_ts_plots("^E_per_Sa[year,pop]")
```

@@

#### Proportion Hatchery Return {.tabset .tabset-pills}

##### Age-3

```{r}
pop_ts_plots("p_hor_a[year,age,pop]", age = 1)
```

##### Age-4

```{r}
pop_ts_plots("p_hor_a[year,age,pop]", age = 2)
```

##### Age-5

```{r}
pop_ts_plots("p_hor_a[year,age,pop]", age = 3)
```

##### Combined

@@

##### Combined

```{r}
pop_ts_plots("Ra_comp_a[year,age,pop]", age = 1)
```

@@

##### Combined

```{r}
pop_ts_plots("Ra_comp_a[year,age,pop]", age = 2)
```

@@

##### Combined

```{r}
pop_ts_plots("Ra_comp_a[year,age,pop]", age = 3)
```
